---
title: "Real data"
author: "Alex Vand"
date: "8/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
```

Read in the data as `toolik_biochem`. Remember, you’ll want to specify here how NA values are stored. Pipe directly into `janitor::clean_names()` following your import code to get all column names into lower snake case.

```{r}
toolik_biochem <- read_csv(here::here("data", "2011_Kling_Akchem.csv"), na = ".")
toolik_biochem <- toolik_biochem %>% janitor::clean_names()
names(toolik_biochem)

# or, alternatively:
# toolik_biochem <- clean_names(toolik_biochem)
# names(toolik_biochem)
```

Create a subset of the data that contains only observations from the “Toolik Inlet” site, and that only contains the variables (columns) for pH, dissolved organic carbon (DOC), and total dissolved nitrogen (TDN) (hint: see `dplyr::select())`. Store this subset as `inlet_biochem`. Make sure to LOOK AT the subset you’ve created.

```{r}
inlet_biochem <- toolik_biochem %>%
  filter(site == "Toolik Inlet") %>% 
  select(p_h, doc_u_m, tdn_u_m)
```


Find the mean value of each column 3 different ways:

- Write a for loop by hand to calculate the mean for each
- Use the `apply()` function to find the mean
- Use the `purrr::map_df()` function to find the mean of each

```{r}
inlet_biochem_mean <- vector(mode = "numeric", length = ncol(inlet_biochem))

for(i in 1:ncol(inlet_biochem)) {
  inlet_biochem_mean[[i]] <- mean(inlet_biochem[[i]], na.rm = TRUE)
}

inlet_biochem_mean
```

```{r}
apply(inlet_biochem, 2, mean, na.rm = TRUE)
```

```{r}
purrr::map_df(.x = inlet_biochem, .f = mean, na.rm = TRUE)
```



